---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# FBRbeta

The FBR method is a highly flexible multi-paramatric method to study fMRI data.
This package was developed to handle lag in fMRI data. This method convoles the
HRF with boxcars for each stimulus event (also called timing). This package 
consist of one general function \code{\link{fbrbetafunc}}, and minor functions.
All minor functions are implemented in this general function.

## Example

This is an example for simulated data. However, this package can handle read
fMRI data, using the function \code{\link[arf3DS4]{readData}}. Important for this
package is that the working directory should be set in the .feat (for FSL)
directory. 

```{r example}
library(FBRbeta)
#Imaging all preprocessed data (obtained via readData("filtered_func_data.nii"))
load("~/Desktop/Rpackage/FBRbeta/data/dat.rda")
dat
#ROI represents the voxels (or for real data for example dat[50, 32, 15,])
ROI = c(9, -3, -7, -9, -7, -5, -9, 2,  7, 13, 20, 9, 4, 2, 7, 7, -2, -3, -5, 0)

# the stimulus presentations are on the following seconds 
##(or real data read.table(file = "custom_timing_files/ev.txt"):
timings = c(2, 6, 8, 10, 12, 14) 

# I want 3 boxes with length 2 
nbox = 3
lenbox = 2

TR = 1

# the desigmatrix for this setup
designmatrix(ROI, timings, nbox, lenbox, TR)
boxtimings <- designmatrix(ROI, timings, nbox, lenbox, TR)

# I want to maximum (or summation) for all beta-values for these designmatrices.
fbrbetafunc(dat, boxtimings, ROI, timings, nbox, lenbox, TR, maximum = T )
```


